---
title: "Intro_to_IRanges"
author: "Xuening"
date: "7/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=F,warning=F)
```

## Introduction to `IRanges`

Package `IRanges` provides fundamental infrastructure and operations for manipulation intervals of sequences.

```{r}
library(IRanges)

# define an IRanges using start and end
my_range <- IRanges(start=20,end=30)
my_range

# define an IRanges with start and width
my_range_width <- IRanges(start=c(20,30,40),width=c(10,10,10))
my_range_width

my_range_width <- IRanges(start=c(20,30,40),width=10)
my_range_width

my_range_end <- IRanges(start=c(1,20),end=30)
my_range_end
```

Notice, width=end-start+1.

## Introduction to Rle
Rle stands for Run length encoding. It computes and stores the lengths and values of a vector or factor. It is a S4 container used to save long repititive vectors efficiently.

```{r}
vec <- c(3,2,2,2,3,3,4,2)
Rle(vec)
```

## IRanges with logical vector
```{r}
IRanges(start=c(F,F,T,T,F,F,F,T,T,T,T))

```

## IRanges with logical Rle
```{r}
gi <- c(T,T,F,F,F,F,T,T,F)
myRle <-Rle(gi) 

# create IRanges with logical Rle
IRanges(start=myRle)
```

## Useful functions

```{r}
# get length of each sequence
width(my_range_width)

# get number of sequences within IRanges
length(my_range_width)
```

