---
title: "Introduction to BS_genome"
author: "Xuening"
date: "7/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=F, warning=F)
```

## About installation
Check versions: use `sessionInfo()` or `packageVersion("PACKAGE_NAME")`.

## Role of S4 in Bioconductor
S3: Most packages in CRAN uses S3 system. It reacts differently, depending on the input, by using a generic function to decide which method to call. Eg. `plot()` can give various plots.
```{r}
methods(plot)
```

Yet the price of flexibility is vagueness. If the user gives an unexpected arguments, all the methods will be tried before the generic function returns an error.  
  
S4: S4 is more object oriented. It defines data first then create functions. The classes are formally defined. Inheritance is clear. Thus other can reuse the framework. This result in more complex implementation.  
  
To check if an object is S4, use `isS4()` or `str()`.  
  
To define a class,  we need to provide the following 3 pieces of information:  
- class name  
- slots (methods/fields)   
- contains (inheritance)  
  
To check formal definition of a class, use `showClass("CLASSNAME")`
```{r}
library(BSgenome)
showClass("BSgenome")
```

*Extends* shows the parent class of `BSgenome`. *Subclasses* shows the classes that inherit from it.  
  
To create an instance of a certain class, use function `new()`.

```{r}
a_genome <- new("BSgenome")
class(a_genome)
is(a_genome)
isS4(a_genome)
```

Since class `BSgenome` has slots `organism`, `provider`, and `seqinfo`, we can retrieve these information using the following accessors:

```{r}
organism(a_genome)
provider(a_genome)
seqinfo(a_genome)
```

## Get yeast genome

BSgenome package contains reference genome of a lot of organisms.
```{r}
available.genomes()
```

We can get yeast genome:
```{r}
library(BSgenome.Scerevisiae.UCSC.sacCer3)
yeast <- BSgenome.Scerevisiae.UCSC.sacCer3
```

and use accessors to retrieve a lot of information.
```{r}
# chromosome number
length(yeast)

# chromosome names
names(yeast)

# length of sequence length
seqlengths(yeast)

# and organism, provider, seqinfo
organism(yeast)
provider(yeast)
seqinfo(yeast)
show(yeast)
```

## Get sequences
```{r}
getSeq(yeast)

# select chromosome sequence by name
getSeq(yeast,"chrM")

# select start/end/width
getSeq(yeast,end=10)
```

We can print sequence. `$` can be used to get specific chromosome :
```{r}
print(yeast$chrM)
```

`nchar()` count characters of a sequence.
```{r}
nchar(yeast$chrM)
```

