---
title: "Intro_to_Biostrings"
author: "Xuening"
date: "7/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE, message=FALSE )
```

## Introduction
Biostrings implements algorithms for fast manipulation of large biological sequences.  
  
Let's see the alphabet of Biostrings.
```{r}
library(Biostrings)
DNA_BASES
RNA_BASES
AA_STANDARD
```

ALPHABET contains more characters and symbols.

```{r}
DNA_ALPHABET
RNA_ALPHABET
AA_ALPHABET
```

## Transcription
```{r}
dna <- DNAString("ATAGGCTATAA")
dna
rna <- RNAString(dna)
rna
```


## Translation
```{r}
head(RNA_GENETIC_CODE)
aa <- translate(rna)
aa

# translate accepts dna
aa <- translate(dna)
aa
```

## Useful functions for string
```{r}
alphabet(dna)
alphabetFrequency(dna)
alphabet(dna, baseOnly=T)
```

```{r}
dna

# get sub-sequence
subseq(dna,end=5)

# get complement
complement(dna)

# get reverse
reverse(dna)

# get reverse complement
reverseComplement(dna)
reverse(complement(dna))
```

## Useful functions for a string set

```{r}
dnaSet <- DNAStringSet(dna,start=c(1,5,9),end=c(4,10,11))
dnaSet
```

```{r}
# number of strings
length(dnaSet)

# length of each string
width(dnaSet)
```

`unlist()` convert a stringSet back to string.

```{r}
seq <- unlist(dnaSet)
length(seq)
```

`rev()` revert the order of each sequence.
```{r}
rev(dnaSet)
```

## Pattern match

```{r}

library(BSgenome.Hsapiens.UCSC.hg19)
hsapiens <- BSgenome.Hsapiens.UCSC.hg19
chrx_seq <- hsapiens$chrX[1000000:1110000]
chrx_seqset <- DNAStringSet(chrx_seq,start=c(1,10000,50000),end=c(1000,11000,51000))
        
# For single sequences
matchPattern(pattern = "ACATGGGCCTACCATGGGAG", 
              subject = chrx_seq, max.mismatch = 1)
        
# For Sets
vmatchPattern(pattern = "ACATGGGCCTACCATGGGAG", 
              subject = chrx_seqset, max.mismatch = 1)
```

## Find palindromes

```{r}
findPalindromes(chrx_seq)
```

