---
title: "More_on_IRanges"
author: "Xuening"
date: "7/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = F,warning=F)
```

## Basics
```{r}
library(IRanges)
ir <- IRanges(5,10)
ir
start(ir)
end(ir)
width(ir)
```

## Intra-range operations

`shift()` shift Irange object by a given step, here 2. 
```{r}
shift(ir,-2)
```

`narrow()` narrow down an IRanges object. If `start`=2, then the returned IRanges starts with second position.

```{r}
ir
narrow(ir,start=2)
```

`flank()` returns the range around the object.
```{r}
# Get the ranges of width 3 before the beginning:
flank(ir,width=3,start=T,both=F)

# Get the ranges of width 3 in the following
flank(ir,width=3,start=F,both=F)

# Get the ranges of width 3 before the beginning, but 3 at the beginning
flank(ir,width=3,start=T,both=T)
```

`resize()` will only return a part from beginning, of given length.

```{r}
resize(ir,1)
```

## Inter-range operations
```{r}
ir <- IRanges(start=c(3,5,17), end=c(10,8,20))
ir
```

`range()` returns the whole span of all ranges.

```{r}
range(ir)
```

`reduce()` collapses the ranges, so that integers are covered by only one range in the output.

```{r}
reduce(ir)
```

`gaps()` gives back the rages of integers which are in `range(ir)` but not covered by any of the ranges in `ir`.

```{r}
gaps(ir)
```

