---
title: "More_on_GRanges_GRangesList"
author: "Xuening"
date: "7/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = F,warning = F)
```

## Define a `GRanges` object
```{r}
library("GenomicRanges")
gr <- GRanges(seqnames=c("ChrZ"),
              ranges=IRanges(start=c(5,10),end=c(35,45)),
              strand="+",
              seqlengths=c(ChrZ=100L))
gr

seqnames(gr)
seqlengths(gr)
```

Functions in `IRanges` can also be applied to `GRanges` object.
```{r}
shift(gr,10)
```

But if we try to shift the range beyond the length of the chromosome, we will get a warining, but we can still get the result.

```{r}
shift(gr,80)
```

To avoid shift the range beyond length of chromosome, we can use `trim()`.

```{r}
trim(shift(gr,80))
```

`mcols()` can be used to retrieve or assign values to metadata columns.

```{r}
mcols(gr)
mcols(gr)$value <- c(-1,4)
gr
```

## Define a `GRangesList` list

To define a GRangesList we can combine 2 or more GRanges object
```{r}
gr2 <- GRanges("ChrZ",IRanges(11:13,51:53),strand="+")
grl <- GRangesList(gr, gr2)
grl
```

## Operations on `GRangesList`

`length()` finds the number of of GRanges object in the GRangesList.
```{r}
length(grl)
```

`elementNROWS()` returns the length of each GRanges. Each GRanges element can be retrieved using "[[]]"
```{r}
elementNROWS(grl)
grl[[1]]
```

`width()` gives an IntegerList, indicating the length of each range in each GRange. 

```{r}
width(grl)
```

`sum()` gives the total length of each GRange
```{r}
sum(width(grl))
```

## `findOverlaps()`

```{r}
gr
gr2
fo <- findOverlaps(gr,gr2)
fo
```

Query is the first argument passed to function `findOverlaps()`. Subject is the second.

```{r}
queryHits(fo)
subjectHits(fo)
```

Notice, this function is strand specific. Only ranges on same chromosome and same strand can have overlaps.
```{r}
strand(gr2) <- "-"
findOverlaps(gr,gr2)
```


## `%over%`

```{r}
strand(gr2) <- "+"
gr %over% gr2
```

